Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\begin{abstract}
Graphs are common data structure used to represent data in which the relation between entities are encoded. A number of graph-based methods and systems have been proposed, varying from biology to recommendation to social network. Most methods have to take partially observed graphs as the input to proceed due to the lack of information. This prevents them from showing promising results. Link prediction becomes an effective paradigm to solve this problem. However, most existing link prediction methods are based on the transitive manner which cannot effectively exploit graph structures. Here we propose a method that first represents each link between two nodes by a graph composed of their neighborhood subgraphs. We then employ a decompositional graph kernel to measure the similarity between links. An empirical experiment on different datasets proves that our proposed method shows the state of the art for link prediction.
\keywords{Link prediction, joint neighborhood subgraphs}
\end{abstract}

@@

In general supervised methods exhibit better accuracies compared to unsupervised methods although incurring in much higher computational and memory complexity costs.
Moreover, most approaches implicitly represent the link prediction problem and the inference used to tackle it as a disjunction over the edges, that is, information on edges is propagated in an additive fashion so that for a node to have $k$ neighbors or $k+1$ does not make a drastic difference.
We claim that this hypothesis is likely putting a cap on the discriminative power of classifiers and therefore we propose a novel supervised method that employs a conjunctive representation. We call the method ''joint neighborhood subgraphs link prediction'' (JNSL). The key idea here is to transform the link prediction task into a binary classification on suitable small subgraphs which we then solve using an efficient graph kernel method.

>>>>

\begin{abstract}
The amount of relational data is increasing rapidly. These datasets are best represented as networks or graphs. A key characteristic of this type of data collections is the sparseness and dynamic nature. A crucial computational task is then the ''link prediction problem'' which allows to suggest possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products to be bought to a customer in a e-commerce recommendation system. Most approaches however do not effectively exploit the topological contextual information available in a neighborhood of each edge. Here we propose to cast the problem as a binary classification task over specific subgraphs and employ efficient graph kernels to solve it.

% Graphs are common data structure used to represent data in which the relation between entities are encoded. A number of graph-based methods and systems have been proposed, varying from biology to recommendation to social network. Most methods have to take partially observed graphs as the input to proceed due to the lack of information. This prevents them from showing promising results. Link prediction becomes an effective paradigm to solve this problem. However, most existing link prediction methods are based on the transitive manner which cannot effectively exploit graph structures. Here we propose a method that first represents each link between two nodes by a graph composed of their neighborhood subgraphs. We then employ a decompositional graph kernel to measure the similarity between links. An empirical experiment on different datasets proves that our proposed method shows the state of the art for link prediction.
\keywords{Link prediction, joint neighborhood subgraphs}
\end{abstract}

@@

In general supervised methods exhibit better accuracies compared to unsupervised methods although incurring in much higher computational and memory complexity costs.
Moreover, most approaches implicitly represent the link prediction problem and the inference used to tackle it as a disjunction over the edges, that is, information on edges is propagated in such a fashion so that for a node to have $k$ neighbors or $k+1$ does not make a drastic difference.
We claim that this hypothesis is likely putting a cap on the discriminative power of classifiers and therefore we propose a novel supervised method that employs a conjunctive representation. We call the method ''joint neighborhood subgraphs link prediction'' (JNSL). The key idea here is to transform the link prediction task into a binary classification on suitable small subgraphs which we then solve using an efficient graph kernel method.
